My Findings

### 2024-07-11 Findings (Shared Folder)/Chapters/PapersReviewed.tex
new notes added

>>>>

\section{Structural Features of Microvascular Networks Trigger Blood Flow Oscillations}{Y. Ben-Ami}{2022, Bulletin of Mathematical Biology}

\subsection{Introduction}

\subsection{Methods}

\subsection{Useful facts}
\begin{itemize}[noitemsep]
	\item Some structural properties of the vascular network can trigger self-sustained oscillations in the blood flow through the network. This has also been shown experimentally \cite{Kimura1996-od}
\end{itemize}

\subsection{I Need to Think More ...}

\subsection{Useful Papers Cited}
